---
title: "Muffin Results - UCL Proj"
author: "Russell Plunkett"
date: "27 January 2019"
output: html_document
---

```{r setup, include=FALSE}
library(car)
library(ggplot2)
library(googledrive)
knitr::opts_chunk$set(echo = TRUE)
```

## Muffin Results

Code for analysing the muffin results captured by team super amazing (but slightly overworked). 

```{r res_create, echo=FALSE, cache=TRUE, cache.path="toto_cache/"}


drive_download("Muffin results", type = "csv", overwrite = TRUE)
results <- read.csv("Muffin results.csv")


results$Operator.f <- factor(results$Operator)
results$Sugar.f <- factor(results$Sugar)
results$Recipe.f <- factor(results$Recipe)
```

## Summary Stats

Some plots to see the difference in the blocks/factors

```{r, echo=FALSE, dependson="res_create", cache.path="toto_cache/"}
qplot(results$Operator.f, results$Height, color = factor(results$Sugar))
qplot(results$Sugar.f, results$Height, color = factor(results$Recipe))
qplot(results$Recipe.f, results$Height, color = factor(results$Sugar))
```


## Variance within factors

Checking for normality within factors and blocks

```{r echo=FALSE, dependson="res_create", cache.path="toto_cache/"}
qqPlot(results$Height)


op1 <-subset(results, Operator == 1)
qqPlot(op1$Height)
op2 <-subset(results, Operator == 2)
qqPlot(op2$Height)
op3 <-subset(results, Operator == 3)
qqPlot(op3$Height)


su1 <-subset(results, Sugar == 1)
qqPlot(su1$Height)
su2 <-subset(results, Sugar == 2)
qqPlot(su2$Height)
# ^ might violate normality assumption

re1 <-subset(results, Recipe == 1)
qqPlot(re1$Height)
re2 <-subset(results, Recipe == 2)
qqPlot(re2$Height)
re3 <-subset(results, Recipe == 3)
qqPlot(re3$Height)
```

There may be one violation of normality in regards to Sugar 2

## Model

Creating the model, and running ANOVA and Summary Stats

```{r model_create, cache=TRUE, dependson="res_create", cache.path="toto_cache/"}
model = lm(results$Height ~ results$Operator.f + results$Sugar.f + results$Recipe.f + results$Operator.f:results$Sugar.f
           + results$Operator.f:results$Recipe.f + results$Sugar.f:results$Recipe.f + results$Operator.f:results$Recipe.f:results$Sugar.f)
Anova(model)
summary(model)
```

And some plots on the model to investigate normality of residuals:

```{r dependson="model_create", cache.path="toto_cache/"}
plot(density(resid(model)))
plot(model)
```

## Post-Hocs

Tukey's HSD were carried out to investigate the significant relationships within factors, between factors, and within interactions.

```{r dependson="res_create", cache.path="toto_cache/"}
TukeyHSD(aov(results$Height ~ results$Operator.f + results$Sugar.f + results$Recipe.f + results$Operator.f:results$Sugar.f
             + results$Operator.f:results$Recipe.f + results$Sugar.f:results$Recipe.f + results$Operator.f:results$Recipe.f:results$Sugar.f))

```










